Open Peer Review

### 2019-10-19 manuscript.Rmd
update manuscript and data

>>>>

# # Using data.table command
# group <- as.data.table(PeerJ_data)
# TEST <- group[group[, .I[df_version == max(df_version)], by=df_link]$V1]

# Select only those reviews for each paper with the highest version (first review)
# For PeerJ the highest number is the first review (for RSOS this is reversed)
PeerJ_data_R1 <- group_by(PeerJ_data, df_link)
PeerJ_data_R1 <- top_n(PeerJ_data_R1, 1, df_version)

TRS_data_R1 <- group_by(TRS_data, df_link)
TRS_data_R1 <- top_n(TRS_data_R1, -1, df_version) #use top_n but specify -1 for bottom 1, or first review.

### general numbers
sum(PeerJ_data_R1$df_masked == 0)
sum(PeerJ_data_R1$df_masked == 1)

sum(TRS_data_R1$df_masked == 0)
sum(TRS_data_R1$df_masked == 1)

# It is useful to select only cases that have a recommendation
TRS_data_complete <- TRS_data[complete.cases(TRS_data$df_recommendation),]

x <- group_by(PeerJ_data_R1, df_recommendation)
x <- summarize(x, m = mean(df_masked))
x

x <- group_by(PeerJ_data_R1, df_recommendation)
x <- summarize(x, m = sum(df_masked))
x

x <- group_by(TRS_data, df_recommendation)
x <- summarize(x, m = mean(df_masked))
x

x <- group_by(TRS_data, df_recommendation)
rowsum(TRS_data_complete[,c(5,7)], group = TRS_data_complete$df_recommendation, na.rm = TRUE)

count(TRS_data$df_recommendation)

x <- summarize(x, m = sum(df_masked))
x <- x[1:4,1:2]
chisq.test(x, correct=FALSE)

x <- x[2:3,1:2]
chisq.test(x, correct=FALSE)
